### 2014-11-10 tex/precise.tex
moving parts of the rules to the supp
unscaled the figures
Fixed field write
updates to equality

\input{summarize-precise}

@@

\subsection{Accessing a Field Reference}
\input{precise-fig}

\begin{figure*}[t]
\begin{center}
\setlength{\tabcolsep}{50pt}
\begin{tabular}[c]{cc}
\usebox{\boxPFAFW} & 
%\scalebox{0.91}{\input{faYHeap.pdf_t}} &
\scalebox{0.91}{\input{fwXHeap.pdf_t}} \\ \\
(a) & (b)
\end{tabular}
\end{center}
\caption{field access for this.y and field write for this.x = this.y}
\label{fig:fHeap}
\end{figure*}

@@

\subsection{Equality and InEquality of References}

\input{precise-eq}

@@

\begin{figure*}
\begin{tabular}[c]{cl}
\usebox{\boxPEQ} & \usebox{\boxPEX} \\ \\
(a) & (b) \\
\end{tabular}
\caption{equals true for this.x == this.y}
\label{fig:eqs}
\end{figure*}

The rewrite rules for check the equals true and equals false when
comparing two references in the symbolic summary heap is shown
in~\figref{fig:eqs}(a). First the equals reference true rewrite rule
returns true if two references $r_0$ and $r_1$ are equal. In GSE this
is a simple comparision of object refrences. In the symbolic summary
heap, however, there we campare sets of constraint location pairs for
each reference. We construct three sets of constraints. The first set,
$\Phi_\alpha$, we check whether under some constraints $\phi_0$ and
$\phi_1$ whether references $r_0$ and $r_1$ respectively point to the
same location $l$.  For all such constraints we create conjunctions of
the constraints $\phi_0 \wedge \phi_1$ and add them to set
$\Phi_\alpha$. The next set of constraints si $\Phi_0$ which contains
the set of constraints from $r_0$ that lead to $l$ such that there is
no constraints under which $r_1$ can point to that $l$.

>>>>

\input{summarize-precise-incomplete}

\begin{figure*}
\begin{tabular}[c]{l}
\scalebox{1.0}{\usebox{\boxPI}} \\
\end{tabular}
\caption{The summary machine, $s ::= \lp\cfgnt{L}\ \cfgnt{R}\ \cfgnt{r}\ \cfgnt{f}\ \cfgnt{C}\rp$, with $s\rsum^*s^\prime =  s \rsum \cdots \rsum s^\prime \rsum s^\prime$.}
\label{fig:symInit}
\end{figure*}

@@

\subsection{Accessing a Field Reference}
\input{precise-fig-incomplete}

\begin{figure*}[t]
\begin{center}
\setlength{\tabcolsep}{60pt}
\hspace*{-35pt}
\begin{tabular}[c]{cc}
\scalebox{1.0}{\usebox{\boxPFAFW}} & 
%\scalebox{0.91}{\input{faYHeap.pdf_t}} &
\scalebox{0.91}{\input{fwXHeap.pdf_t}} \\ \\
(a) & (b)
\end{tabular}
\end{center}
\caption{field access for this.y and field write for this.x = this.y}
\label{fig:fHeap}
\end{figure*}

@@

\subsection{Equality and InEquality of References}
\input{precise-eq}

\begin{figure*}
\begin{tabular}[c]{c}
\scalebox{1.0}{\usebox{\boxPEQ}} \\
% & \usebox{\boxPEX} \\ \\
%(a) & (b) \\
\end{tabular}
\caption{FIXME: I desperately need a caption!}
\label{fig:eqs}
\end{figure*}

@@

The rewrite rules to compare two references in the symbolic summary
heap are shown in~\figref{fig:eqs}. The equals references-true rewrite
rule returns true when two references $r_0$ and $r_1$ are equal. In
GSE this is a simple comparision of two concrete object references. In
the symbolic summary heap, however, we compare sets of constraint
location pairs pointed to by each reference. Let us consider the
equals reference-true rewrite rule. Here, we construct three sets of
constraints. To construct the first set, $\Phi_\alpha$, we check if
there exist constraint location pairs $(\phi_0, l_0) \in L(r_0)$ and
$(\phi_1, l_1) \in L(r_1)$ such that $l_0$ and $l_1$ are the same.
For all such constraints we create conjunctions of the constraints
$\phi_0 \wedge \phi_1$ and add them to set $\Phi_\alpha$. Intutively
these represent the constraints under which $r_0$ and $r_1$ point to
the same location in the heap. The next set of constraints is $\Phi_0$
which contains a constraints under which $r_0$ points to a
corresponding location $l_i$ such that $r_1$ \emph{does not} point to
$l_i$ under any constraint. Inversely, the set of constraints $\Phi_1$
contains the set of constraints under which $r_1$ points to a
corresponding location $l_j$ and $r_0$ \emph{does not} point to $l_j$
under any constraint.

To the global constraint we add the disjunction of the constraints in
$\Phi_\alpha$ to indicate that if any of the constraints are
satisfiable, then references $r_0$ and $r_1$ can be true. Furthermore,
we had to the global heap constraint, $\phi_g^\prime$, the
conjunctions of negations to the constraints in $\Phi_0$ and
$\Phi_1$. This indicates for locations that are not common to the
references, the negations of their constraints are satisfiable. Before
the rewrite rule returns true the satisfiability of the updated global
heap constraint is checked.

Consider the example in~\figref{fig:initHeap}(c), where we would like
to check if $r_1^i$ and $r_2^i$ are equal. The set of constraint locations 
pairs of the two references are:

\[
L(r_1^i) = \{ (\phi_{1a}\; l_\mathit{null})\; (\phi_{1b}\; l_1) \} 
\]
\[
L(r_2^i) = \{ (\phi_{2a}\; l_\mathit{null}),\; (\phi_{2b}\; l_2),\; (\phi_{2c}\; l_1) \} \\
\]

\noindent{The three constraint sets are:}

\[
\Phi_\alpha = \{ (\phi_{1a}\; \wedge\; \phi_{2a} ) (\phi_{1b}\; \wedge\; \phi_{2c} ) \}\;
\Phi_0 = \{ \}\; \Phi_1 = \{ \phi_{2b}\} \\
\]

\noindent{Finally the global constraint is} 
\[
\phi^\prime = \mathit{true} \wedge  (\phi_{1a}\; \implies\; \neg\phi_{2a} )\wedge (\phi_{1b}\; \implies\; \neg\phi_{2c} )  \wedge \phi_{2b}
\]
